Designing and Developing a Personalised Recommender System

### 2021-02-05 paper/paper.tex
going to filter restaurants by nearest city

\subsection{Input interface}
The input interface is the command line.
The program offers users opportunites to input information about themselves,
as well as make choices from a selection of items which the system provides or suggests.

>>>>

\subsection{Input interface}
The input interface is the command line.
The program offers users opportunities to input information about themselves,
as well as make choices from a selection of items which the system provides or suggests.
